---
title: "Home"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

#Load libraries


```{r}
# load libraries
library(knitr)
opts_chunk$set(warning=F,message=F,fig.width = 11,fig.height = 5,cache=F)

library(tidyverse)
library(purrr)
library(janitor)

```

 # read in data
```{r}

#system.time(    
#  read_csv('vijaya_data/all.csv.gz') %>%
#    clean_names () %>% 
#    { . } -> all
#  )

library("RPostgreSQL")

# loads the PostgreSQL driver
  # creates a connection to the postgres database
  # note that "con" will be used later in each connection to the database
  con <- dbConnect(dbDriver("PostgreSQL"), 
                   dbname = "vijaya_vaed",
                   host = "localhost", port = 5432,
                   user = "dewoller", password  = Sys.getenv('PASSWD'))

# check for the cartable

df_vaed  = dbReadTable(con, name='vaed' ) %>% as_tibble()

df_audit  = dbReadTable(con, name='audit' ) %>% as_tibble()

```


# Explore paramemters

```{r }

df_vaed %>% 
  select( starts_with('diag' ) ) %>%
  gather( pos, diag ) %>%
  filter( !is.na( diag )) %>% 
  { . } -> df_vaed_diag_long



df_vaed %>%
  select( starts_with('oper' ) ) %>%
  gather( pos, oper ) %>%
  filter( !is.na( oper )) %>% 
  { . } -> df_vaed_oper_long

df_vaed %>% distinct( age_group ) %>% c()

cat('## number of distinct PDx')
df_vaed_diag_long %>%
  filter( pos == 'diag1') %>%
  count( diag, sort=TRUE) %>% 
  dim() %>% 
  pluck(1)

```

# Distinct value

```{r Number of distinct values}

df_vaed_diag_long %>%
  count( diag, sort=TRUE) %>% 
  dim() %>% 
  pluck(1)


df_vaed_oper_long %>%
  count( oper, sort=TRUE) %>% 
  dim() %>% 
  pluck(1)

```

# Audit data Columns

```{r Audit_data}


df_audit %>%
  select( starts_with('hospital')) %>%
  names()

df_audit %>%
  select( starts_with('audit')) %>% 
  names()

```

# What fields are not matching audit hospital pairs


```{r }

df_audit %>%
  select( 
         -starts_with('hospital')
         , -starts_with('audit')
         ) %>% names()

df_audit %>% 
  select( ends_with('flag')) %>% names()
```

# make audit data long

```{r }

df_audit %>%
  mutate( row = row_number()) %>%
  select( row, starts_with('audit')
        , starts_with('hospital')) %>%
  gather( code, value, -row ) %>%
  separate( code, into=c('which', 'col' ), sep='_', n=2, extra='merge') %>%
  spread( which,value) %>% 
  filter( !is.na( hospital) & !is.na( audit )) %>%
  { . } -> df_audit_long


```

# How many audit records alltogether, and 


```{r }
df_audit %>% dim() %>% pluck(1)


```

# How many audit records have some sort of change


```{r }
df_audit_long %>%
  filter( audit != hospital) %>% 
  distinct(row) %>%
  dim() %>%
  pluck(1)

```
About 1/2 of audited records have corrections

# How many corrections in each of the categories 


```{r }

df_audit_long %>%
  filter( startsWith( col, 'admission' )) %>%
  filter( audit != hospital) %>% 
  distinct(row) %>%
  dim() %>%
  pluck(1)

df_audit_long %>%
  filter( startsWith( col, 'diagnosis_code' )) %>%
  filter( audit != hospital) %>% 
  distinct(row) %>%
  dim() %>%
  pluck(1)

df_audit_long %>%
  filter( startsWith( col, 'proc' )) %>%
  filter( audit != hospital) %>% 
  distinct(row) %>%
  dim() %>%
  pluck(1)

```

# how much of the difference is merely a rearrangement of the codes?

```{r Audit_difference}

df_audit_long %>%
  filter( startsWith( col, 'diagnosis_code' )) %>%
  filter( audit != hospital) %>% 
  group_by( row ) %>%
  summarise( audit_codes = paste( sort( audit ), collapse=' '), 
            hospital_codes =paste( sort( hospital ), collapse=' ') ) %>% 
  { . } -> df_sorted_differences_diag

df_audit_long %>%
  filter( startsWith( col, 'proc' )) %>%
  filter( audit != hospital) %>% 
  group_by( row ) %>%
  summarise( audit_codes = paste( sort( audit ), collapse=' '), 
            hospital_codes =paste( sort( hospital ), collapse=' ') ) %>% 
            { . } -> df_sorted_differences_proc

cat('## Errors that are not mere rearrangments of Procedures')
df_sorted_differences_proc %>%
  filter( hospital_codes != audit_codes ) %>%
  distinct( row ) %>% dim() %>% pluck(1)

cat('## Errors that are not mere rearrangments of Diagnosis codes (excluding prefix)')
df_sorted_differences_diag %>%
filter( hospital_codes != audit_codes ) %>%
  distinct( row ) %>% dim() %>% pluck(1)



df_audit_long %>%
  filter( audit != hospital) %>% 
  filter( startsWith( col, 'diagnosis' )) %>%
  mutate( type = ifelse( startsWith( col, 'diagnosis_code'), 'D', 'P' ), 
         pos = str_replace_all( col, '[a-z_]','') %>% as.numeric()) %>%
  select( -col) %>%
  gather( institution, code, -row, -type, -pos ) %>%
  spread( type, code ) %>%
  mutate( P = ifelse( is.na(P), ' ', P ),
         full = paste( P,D)) %>%
  select( -D, -P ) %>%
  spread( institution, full) %>%
  group_by( row ) %>%
  summarise( audit_codes = paste( sort( audit ), collapse=' '), 
            hospital_codes =paste( sort( hospital ), collapse=' ') ) %>% 
  { . } -> df_sorted_differences_diag_prefix

cat("## number of cases where there is a problem with prefix and/or codes, separate from rearrangment")

df_sorted_differences_diag_prefix %>%
filter( hospital_codes != audit_codes ) %>%
  distinct( row ) %>% dim() %>% pluck(1)

```


```{r }
```


